Local Spectral Clustering of Density Upper Level Sets

### 2019-06-20 neurips/local_spectral_density_clustering_arxiv.tex
fixed one typo

To do so, we split the interval $[0,1]$--based on a number $\mu = as(G)$ for some $0 < a < 1$ to be specified later--into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$. Let $\ell_{\mu}(x)$ be the linear interpolator between $h_z^{(0)}(\mu)$ and $h_z^{(0)}(1 - \mu)$, 
\begin{equation*}
\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(1 - \mu).
\end{equation*}

>>>>

To do so, we split the interval $[0,1]$ into the subinterval $[\mu, 1 - \mu]$ and the remainder $[0,\mu) \cup (1 - \mu, 1]$, where $\mu = as(G)$. Let $\ell_{\mu}(x)$ be the linear interpolator between $h_z^{(0)}(\mu)$ and $h_z^{(0)}(1 - \mu)$, 
\begin{equation*}
\ell_{\mu}(x) = \frac{1 - \mu - x}{1 - 2\mu} h_z^{(0)}(\mu) + \frac{x - \mu}{1 - 2\mu}h_z^{(0)}(1 - \mu).
\end{equation*}
